Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-29 writing/DraftExposurePaper/DraftExposurePaper.Rmd
set custom cutoffs for distance and rainfall count maps

```{r echo = FALSE, warning=FALSE}
data(closest_dist)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE}
rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 500,
                             days_include = c(-1, 0, 1))
rain_1000 <- rain_exposure %>%
        arrange(desc(tot_precip)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.factor(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
rain_1000$value <- as.numeric(rain_1000$value)
map_1000 <- county_choropleth(rain_1000,
                              title = "Hits for top 1000 Storm-County Pairs\nfor Rain > 75 mm",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE}
distance_count <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value))
map_dist_count <- county_choropleth(distance_count, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_count + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips, value = count) %>%
              mutate(region = as.numeric(region), value = as.numeric(value))
map_counts <- county_choropleth(rain_count,
                                title = "Hits by County\nfor Rain > 75 mm",
                                legend = "Hits per County", num_colors = 9,
                                state_zoom = eastern_states)
map_counts + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

```{r}
exposure_name <- c("Rain_Exposure", "Distance_Exposure")
count <- c(sum(rain_count$value), sum(distance_count$value))
exposure_table <- cbind(exposure_name, count)
exposure_table <- data.frame(exposure_table)
exposure_table %>%
        mutate(exposure_name = gsub("_", " ", exposure_name)) %>%
        kable(col.names = c("Exposure Criteria", "Total # exposed counties"), 
              caption = "Total number of county hits based on rain, distance, and wind exposures")
```

>>>>

```{r echo = FALSE, warning=FALSE, message=FALSE}
data(closest_dist)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) %>%
        arrange(desc(count)) %>%
        slice(1:1000)
distance_1000$value <- cut(distance_1000$count, c(0, 5, 8, 12, 15, 18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15", "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 7,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 500,
                             days_include = c(-1, 0, 1))
rain_1000 <- rain_exposure %>%
        arrange(desc(tot_precip)) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) %>%
        arrange(desc(count)) %>%
        slice(1:1000)
rain_1000$value <- cut(rain_1000$count, c(0, 3, 6, 9, 12, 15, 17), 
                   labels = c("0-3", "4-6", "7-9", "10-12", "13-15", "16-17"), 
                   include.lowest = TRUE)
map_1000 <- county_choropleth(rain_1000,
                              title = "Hits for top 1000 Storm-County Pairs\nfor Rain > 75 mm",
                              legend = "Hits per County", num_colors = 6,
                              state_zoom = eastern_states)
map_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
distance_count <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) %>%
        arrange(desc(count))
distance_count$value <- cut(distance_count$count, c(0, 5, 8, 12, 15, 18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15", "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
map_dist_count <- county_choropleth(distance_count, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 7,
                              state_zoom = eastern_states)
map_dist_count + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
rain_count$value <- cut(rain_count$count, c(0, 3, 6, 9, 12, 15, 17), 
                   labels = c("0-3", "4-6", "7-9", "10-12", "13-15", "16-17"), 
                   include.lowest = TRUE)
map_counts <- county_choropleth(rain_count,
                                title = "Hits by County\nfor Rain > 75 mm",
                                legend = "Hits per County", num_colors = 6,
                                state_zoom = eastern_states)
map_counts + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

```{r}
exposure_name <- c("Rain_Exposure", "Distance_Exposure")
count <- c(sum(rain_count$count), sum(distance_count$count))
exposure_table <- cbind(exposure_name, count)
exposure_table <- data.frame(exposure_table)
exposure_table %>%
        mutate(exposure_name = gsub("_", " ", exposure_name)) %>%
        kable(col.names = c("Exposure Criteria", "Total # exposed counties"), 
              caption = "Total number of county hits based on rain, distance, and wind exposures")
```
